Generating the Blueprints of Java Ecosystem

### 2015-02-22 msr.tex
one footnote url left

  \item \textbf{JDepend} \textit{(jdep)}\footnote{\url{http://clarkware.com/software/JDepend.html}} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.

>>>>

  \item \textbf{JDepend} \textit{(jdep)}~\cite{JDEPEND} is an source tool that analyses {\sc jar} files that contain compiled Java classes and calculates a series of design metrics.
